---
title: "Model_Creation"
author: "Jenny Spencer"
date: "9/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sessionInfo()



rm(list=ls())

library(EpiModel)   #the primary package we will be using to make our models 
library(ndtv)       #for the fancy videos
library(readxl)     #read in excel files 
library(tidyverse)  #Includes a number of shortcuts for data manipulation
library(beepr)      #makes the code beep when you get to it. Beep. 
library(kableExtra)  #for making tables look nice
library(mc2d)        #for using pert distribution
library(dplyr)      #for data manipulation

```

## Creating a Network

This is for testing the mechanics around network creation with my bisexual model 

First I want to create a network of 1000 people. Then I will give them attributes

  1) Sex - M/F this will be 50/50 
  
  2) Sexual Behavior- this will be opposite sex, same sex, or bisexual and this distribution will vary by individual sex 
      6% women bi, 2% women samesex, 92% women oppsex
      2% men bi,   2% men samesex,   96% men oppsex      
      
  3) Age Distribution- Assumed to be equal by sex and sexual behavior
      
```{r network_initiatlize}

# # # # Network Size and initialization # # # # # 

#Create a nework of 50/50 men and women 
n                  <- 500

#Create populations for each size of our groups
n.msmo             <- n

#Positional Preferences
pct.pos_r          <- .16   
pct.pos_i          <- .28 
pct.pos_v          <- .56 


#Network with n people, partnerships are not directed 
net1              <- network.initialize(n, directed=FALSE)


# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex",   c(rep("M", n)))

# # # # # # SEXUAL BEHAVIOR  # # # # 
#and a more complex one 
#set.vertex.attribute(net1, "behavior", c(rep("MM", n.msmo)))   


#and a more complex one 
set.vertex.attribute(net1, "position", c(rep("Receptive", (pct.pos_r*n.msmo)), 
                                         rep("Insertive", (pct.pos_i*n.msmo)), 
                                         rep("Versatile", (pct.pos_v*n.msmo))))   # position

# # # # # #  AGE   # # # # 

#calc age dist 
l.age              <- c( "<1", "1-4", "5-9", "10-14", "15-20", "20-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59",   
                         "60-64", "65-69", "70-74", "75-79",  "80-85", "85+")

#make upper and lower limit variables- the actual age will be draw from a distribution within these so these will line up exactly. 
ll.age             <- c( 0,   1,   5,   10,  15,  20,  25,  30,  35,  40,  45 , 50,   55,   60,   65,   70,   75,  80,  85)
ul.age             <- c( 1,   5,   10,  15,  20,  25,  30,  35,  40,  45,  50,  55,   60,   65,   70,   75,   79,  85,  90)

i.age_dist         <-c(.04, .05, .05, .06, .06, .06, .06, .07, .07, .07, .06, .06, .06, .06, .06, .04, .04, .02 ,.01) 


#add age category
age_group          <-  c(rep(l.age, (n.msmo*i.age_dist)))
#Three step process to add ages by year- 
    #First define upper and lower bounds
                 age_ll             <-  c( rep(ll.age, (n.msmo*i.age_dist)))
                 
                 age_ul             <-  c(rep(ul.age, (n.msmo*i.age_dist)))
                 
  
                
#Then draw n uniform distributions                                     
draw_age           <- runif(n, min=0, max=1)
age_yrs            <- draw_age

matrix             <- matrix(c(age_group, draw_age, age_ll, age_ul), ncol=4)

#And rescale each to within the assigned bounds
#If you get an error in this code, it may be because your probabilities don't add up to one. 
for(i in 1:n) {
      age_yrs[i]   <- scales::rescale(draw_age[i], to = c(age_ll[i], age_ul[i]), from = c(0, 1))
}

#Finally, add specific age (years) to attribute
set.vertex.attribute(net1, "age", round(age_yrs, 1)) 

hist(get.vertex.attribute(net1, "age"))


#Randomly assign everyone an age for onset of sexual behavior- this is the age when they can start finding partners so it will be slightly younger than the age at which they are first partnered

age_active                 <- c(rpert(n.msmo, min=9, mode=14, max=40, shape=10))

set.vertex.attribute(net1, "age.actv", age_active)

check.sex.active           <- ifelse(age_yrs>=age_active, 1, 0)


set.vertex.attribute(net1, "sex.actv", check.sex.active)

```


Additional model functions

Three additional modules are described here

1) Births- new individuals are born into the population at **birth.rate** 

2) Deaths- Individuals exit the population by age-specific **death.rate** 

3) Aging- Each time step, individuals age one week. The aging calculation also updates age group. 

```{r functions}


d.lifetable        <- data.frame(read_excel("./_2A_Inputs/mortality.xlsx", sheet="Sheet1")) 


mortality_rate_m   <- d.lifetable$Male

# rate per person, per week

mrm_pp_pw          <- mortality_rate_m / 1e5 / 12

# Build out a mortality rate vector

age_spans          <-c(1,4,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5)

mr_vec_m           <- rep(mrm_pp_pw, times = age_spans)

mort_all           <- (data.frame(c(0:89), mr_vec_m))
                        colnames(mort_all) <-  c("Age", "Male")
                        1-(8/27)
                        
                  
#Create probability of regression of anal HPV
#Data from Nyitray 2016- Clinical Infetious Disease
#Scale and shape parameters were derived in excel because I'm basic. 

d.Nyitray          <- data.frame("months"=c(0,6,12,18,24), "persist"=c(1, 0.49, 0.42, 0.32, 0.3))
d.Ingles           <- data.frame("months"=c(0,12,24,36), "persist"=c(1, 0.45, 0.2, 0.14))

v.time             <- seq(0,36)                                                
a.weibull          <- pweibull(v.time, 0.4, scale = 17.2, log.p = FALSE)
g.weibull          <- pweibull(v.time, 0.6, scale = 14.2, log.p = FALSE)

w.for_graph        <- data.frame("time"=c(v.time), "inf_a"=1-a.weibull, "inf_p"=1-g.weibull)


ggplot() +
  geom_point(aes(x=d.Nyitray$months, y=d.Nyitray$persist), color="red", shape=15, size=4) + 
  geom_line(aes(x=w.for_graph$time, y=w.for_graph$inf_a), lstyle="dash") +    theme_classic() + 
  ylim(0,1) + ggtitle("Comparison of Observed vs. Fitted Anal HPV Clearance") + 
  ylab("Persistant Infection") + xlab("Months Since Infected")

ggplot() +
  geom_point(aes(x=d.Ingles$months, y=d.Ingles$persist), color="blue", shape=15, size=4) + 
  geom_line(aes(x=w.for_graph$time, y=w.for_graph$inf_p), lstyle="dash") +    theme_classic() + 
  ylim(0,1) + ggtitle("Comparison of Observed vs. Fitted Penile HPV Clearance") + 
  ylab("Persistant Infection") + xlab("Months Since Infected")

rec.month.A       <- (a.weibull[2:37] - a.weibull[1:36])      
rec.month.G       <- (g.weibull[2:37] - g.weibull[1:36])   
```


Then we create our target stats. The edges calculations are a little complex so these can be see in edges_calculations.xlsx in the inputs folder. This file outputs edges by sexual behavior combinations in the order that our equation expects them. We add the total number of edges here also. 

```{r target_stats}

edges              <- (n*0.635*0.5)   

#Then stats based on this- first edges total, the concurrent, then all possible combinations that should be impossible 
#(ie, two men who only have sex with women can never have a partnership)
# Impossible combinations: FB.FM, FF.FM, FM.FM, FF.MB, FF.MF, MB.MF, MF.MF, FB.MM, FF.MM, FM.MM, MF.MM

targets            <- c( edges,         #total edges
                       (n*.10),          #concurrent nodes  
                       edges*4.6,       #age assortiveness
                        0,              #no receptive only x receptive only partnerships
                        0,              #no insertive only x insertive only partnerships
                        0,              #no sex if not sexually active
                   (edges*pct.pos_v*2))   #increase receptive partnerships
```

```{r model_fit}

set.seed(041788)

coef.diss          <- dissolution_coefs( dissolution = (~offset(edges)), # + offset(nodemix("combo", levels2=c(-13)))), 
                                          duration  = c(73.5), #should be 73.5
                                             d.rate = mean(mort_all$Male))


 f.form            <- ~edges +  
                       concurrent  +
                       absdiff("age") + 
                       nodemix("position", levels2=c(1,3))  + 
                       nodefactor("sex.actv", levels=c(1))  +
                       nodefactor("position", levels=c(3))  
	
	
#Now make the formation model which is conditional on the dissolution model 

fit1               <- netest(net1, 
                            formation    = f.form, 
                            target.stats = targets, 
                            #edapprox     = FALSE,
                            coef.diss    = coef.diss) 

summary(fit1)

  #dx.static     <- netdx(fit1, nsims = 1000, dynamic=FALSE)
  #dx.static
  
  
```

```{r simulate, echo=FALSE}
set.seed(041788)

#Simulate our model given the formation and dissolution we've established. Run for 1000 steps but just 1 simulation of it
dx_sim             <- netdx(fit1, nsteps = (1000), nsims = 3, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodefactor("position", levels=c(1,2,3)) + absdiff("age"))

#show what happened as a table
dx_sim$stats.table.formation

#mcmc.diagnostics(fit1$fit) 
```

```{r model_diagnostics}
#we can also make fit graphs 
plot(dx_sim, type  = "formation" )

plot(dx_sim, type  = "duration")
plot(dx_sim, stats = c("edges", "concurrent"))

#Check concurrency by group 
tel_inf               <- data.frame(behav= get.vertex.attribute(net1, "behavior"),ID= (get.vertex.attribute(net1, "vertex.names")))
tel_dx                <- as.data.frame(dx_sim, sim = 1) 
tel_dx$ID             <- tel_dx$tail
together1             <- merge(tel_inf, tel_dx, by.y="ID")
  
tel_dx$ID             <- tel_dx$head
together2             <- merge(tel_inf, tel_dx, by.y="ID")

together              <-rbind(together1,together2)
together$count        <- 1
together              <- together[which(together$terminus.censored==TRUE),]   

count_by_ID           <-aggregate(together[11], list(together$ID, together$behav), sum)

MM_conc               <- length(count_by_ID$count[which(count_by_ID$count>=2 & count_by_ID$Group.2=="MM")])/n.msmo

```

```{r infection}

source("./05_Model_Functions.R")
#source("./05_Model_Functions_delete_nodes_debug.R")
  simtime          <- 800
  n.sims           <- 3


 # Parameterizing an SIS epidemic
 param             <- param.net( inf.prob = 0.0001,
                          mortality.rates = (mort_all),
                               birth.rate = (mean(mort_all$Male)), 
                               rec.rate.a = rec.month.A, 
                               rec.rate.g = rec.month.G, 
                               rec.rate   = .00001,
                                 act.rate = 5.5, 
                               inf.prob.r = 0.33, 
                               inf.prob.i = 0.05)
 order_list      <- c("infection.FUN", "aging.FUN", "departures.FUN", "recovery.FUN", "arrivals.FUN", "epi.FUN")
 
 # Initial conditions
 init              <- init.net(i.num = n*0.1)
 
 start.time        <- Sys.time()
 # Control settings
 control           <- control.net(type = "SIS", 
                                 nsims = n.sims, 
                                ncores = 8,
                                nsteps = simtime, 
                         infection.FUN = f.inf_msm,
                             aging.FUN = age.func,
                          recovery.FUN = f.recovery,
                        departures.FUN = d.func,
                          arrivals.FUN = b.func,
                               epi.FUN = epi.func, 
                        keep.tedgelist = FALSE,
                         keep.tnetwork = TRUE,  
                      #    delete.nodes = TRUE, 
                                depend = TRUE,
                      #    module.order = order_list,
                               verbose = TRUE)

 
# Run the network model simulation with netsim
sim_short          <- netsim(fit1, param, init, control)

 stop.time          <- Sys.time()
(total.time        <- stop.time - start.time)

#plot(sim_short)

out_sim            <- as.data.frame(sim_short)
tel_sim            <- as.data.frame(sim_short$network$sim1) 


#Finally, add specific age (years) to attribute
 age_out           <- get.vertex.attribute(sim_short$network$sim1, "age") 
 pos_out           <- get.vertex.attribute(sim_short$network$sim1, "position") 
 sex_out           <- get.vertex.attribute(sim_short$network$sim1, "sex.actv") 
 sex_age           <- get.vertex.attribute(sim_short$network$sim1, "age.actv") 


  

#  hist(age_out[sex_out==1])

#  hist(age_out[sex_out==0])

#  hist(sex_age, density=4.5, main=("MSM age of sexual onset (modeled)"), xlab = "Age")
  

 ggplot()+ geom_point(aes(x=sex_age, y=age_out, col=sex_out))



 hist(get.vertex.attribute(sim_short$network$sim1, "age"))

     n2              <- network.size(sim_short$network$sim1)
     
     beep(2)
     

```

```{r plot1}


  time               <- c(seq(1, simtime,1))/12
                             


  f.minmax           <- function(stat) {
  stat_mean          <-apply(stat, 1, mean)*100
  stat_max           <-apply(stat, 1, max)*100
  stat_min           <-apply(stat, 1, min)*100

 stat_out            <- data.frame(mean=stat_mean[2:simtime], max=stat_max[2:simtime], min=stat_min[2:simtime], time=(seq(2, simtime, 1)/12))
 
  return(stat_out)
  }
  
  overall            <- f.minmax(sim_short$epi$prv_a.MM)
  overall$group      <- "Overall"
  
  versatile          <- f.minmax(sim_short$epi$prv_a.v)
  versatile$group    <- "Versatile"
   
  receptive          <- f.minmax(sim_short$epi$prv_a.r)
  receptive$group    <- "Receptive"
  
  insertive          <- f.minmax(sim_short$epi$prv_a.i)
  insertive$group    <- "Insertive"
  
  
  together_a         <- rbind(overall, versatile, receptive, insertive)

  
   
    ggplot() + 
    geom_line(aes(y=together_a$mean , x=together_a$time, color=together_a$group), size=1) + 
        geom_ribbon(aes(ymin= together_a$max, 
                        ymax= together_a$min, 
                        x=together_a$time, fill=together_a$group), alpha=0.5)  +
                          theme_classic() +
                   ylim(0,100) +
                scale_color_manual(name="Sexual Behavior Group", 
                                  breaks=c("Insertive", "Receptive", "Versatile", "Overall"), 
                                  values=c("Insertive"="#1b9e77", 
                                           "Receptive"="#7570b3", 
                                           "Versatile"="#d95f02",
                                           "Overall"="black")) +
      
                 scale_fill_manual(name="Sexual Behavior Group", 
                                  breaks=c("Insertive", "Receptive", "Versatile", "Overall"), 
                                  values=c("Insertive"="#1b9e77", 
                                           "Receptive"="#7570b3", 
                                           "Versatile"="#d95f02",
                                           "Overall"="black")) +
                  theme(panel.background = element_rect(fill = NA),
                    plot.title = element_text(size = 10, face = "bold")) +
                     ggtitle("Prevalence of HPV Among MSM: Anal HPV") +
                     ylab("Percent Infected (%)") + 
                     xlab("Time (Years)")  + 
                     geom_linerange(aes(x=(simtime/13), ymin=9.8, ymax=15.4), size=2, color="black")

  
    overall            <- f.minmax(sim_short$epi$prv_g.MM)
  overall$group      <- "Overall"
  
  versatile          <- f.minmax(sim_short$epi$prv_g.v)
  versatile$group    <- "Versatile"
  
  receptive          <- f.minmax(sim_short$epi$prv_g.r)
  receptive$group    <- "Receptive"
  
  insertive          <- f.minmax(sim_short$epi$prv_g.i)
  insertive$group    <- "Insertive"
  
  
  together_g         <- rbind(overall, versatile, receptive, insertive)
  
  
      ggplot() + 
    geom_line(aes(y=together_g$mean , x=together_g$time, color=together_g$group), size=1) + 
        geom_ribbon(aes(ymin= together_g$max, 
                        ymax= together_g$min, 
                        x=together_g$time, fill=together_g$group), alpha=0.5)  +
                          theme_classic() +
                   ylim(0,100) +
                scale_color_manual(name="Sexual Behavior Group", 
                                  breaks=c("Insertive", "Receptive", "Versatile", "Overall"), 
                                  values=c("Insertive"="#1b9e77", 
                                           "Receptive"="#7570b3", 
                                           "Versatile"="#d95f02",
                                           "Overall"="black")) +
      
                 scale_fill_manual(name="Sexual Behavior Group", 
                                  breaks=c("Insertive", "Receptive", "Versatile", "Overall"), 
                                  values=c("Insertive"="#1b9e77", 
                                           "Receptive"="#7570b3", 
                                           "Versatile"="#d95f02",
                                           "Overall"="black")) +
                  theme(panel.background = element_rect(fill = NA),
                    plot.title = element_text(size = 10, face = "bold")) +
                     ggtitle("Prevalence of HPV Among MSM: Genital HPV") +
                     ylab("Percent Infected (%)") + 
                     xlab("Time (Years)") + 
                     geom_linerange(aes(x=(simtime/13), ymin=7.2, ymax=17.2), size=2, color="black")

```

```{r plot_by_age}



```

