---
title: "Test_just_samesex"
author: "Jenny Spencer"
date: "1/16/2020"
output: html_document
---


# Epimodel Fit Issues 

```{r setup}
#Just MSM
rm(list=ls())

library(EpiModel)   #the primary package we will be using to make our models 
library(beepr)
set.seed(041788)


#controls
n.sim      <- 3
n.steps    <- 500
```


## Test 1: MSM and WSW only 

We start with same-sex only (WSW and MSM) partnerships. We make each of these groups 50% of the total population. We assume a mean density of 70% and a concurrency rate of 5%. Mean relationship duration is 60 months. 

We set a limitation that WSW and MSM individuals cannot partner with each other- only within group partnerships are allowed. 


We start with same-sex only (WSW and MSM) and opposite-sex only (WSM and MSW) partnerships. To start we make each of these grousp 25% of the total population. We assume a mean density of 80% and a concurrency rate of 5%. Mean duration is 60 months. 

We define impossible combinations of sexual partnerships using nodemix on sexual behavior categories so that MSM can only partner with each other, WSW can only partner with each other and MSW/WSM can only partner across groups. 


```{r create_network1, warning=FALSE, message=FALSE}
# # # # # # # # # # # #  Create Network  # # # # # # # # # # # # # # # # 

#Create a nework of 50/50 men and women 
n                  <- 20000

#Create populations for each size of our groups
n.msmo             <- n* 0.5
n.wswo             <- n* 0.5

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo)))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo)))   # then for men


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Define number of expected edges (density=0.7)
edges              <- (n *.7 * 0.5)   

#Overall concurrency is 5% 
concurrency        <- .05

#Formation model 
f.form             <- ~edges + concurrent +  nodemix("behavior", levels2=c(2))

#Target stats
targets            <- c( edges ,            # total edges
                       (n*concurrency) ,    # concurrent
                        0)                  # no FF xMM relationships

#Dissolution model 
coef.diss          <- dissolution_coefs( dissolution = (~offset(edges)), 
                                           duration  = c(60.0)) 


#Now make the formation model which is conditional on the dissolution model 
fit1               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit1)
```

### FIT 1:  MSM and WSW only 

Now we run a test of this model to see how we fit. 

```{r simulate1}
#Simulate our model given the formation and dissolution we've established. 
dx_sim1             <- netdx(fit1, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior") ) #+ degree(0:3))

#show what happened as a table
dx_sim1$stats.table.formation
plot(dx_sim1)
plot(dx_sim1, type  = "duration")

density_FF        <- (dx_sim1$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MM        <- (dx_sim1$stats.table.formation$`Sim Mean`[5]/n.msmo)*2

(statsout1         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= c((round(density_FF,3)), NA, (round(density_MM,3))), 
                                "density target"=c(0.7, NA , 0.7)))

```


## Test 2: 4 groups, equal size, no restrictions 

We start with same-sex only (WSW and MSM) and opposite-sex only (WSM and MSW) partnerships. To start we make each of these grousp 25% of the total population. We assume a mean density of 80% and a concurrency rate of 5%. Mean relationship duration is 60 months. 

We define impossible combinations of sexual partnerships using nodemix on sexual behavior categories so that MSM can only partner with each other, WSW can only partner with each other and MSW/WSM can only partner across groups. 


```{r create_network2 , warning=FALSE , message=FALSE}
# # # # # # # # # # # #  Create Network  # # # # # # # # # # # # # # # # 

#Create populations for each size of our groups
n.msmo             <- n* 0.25 
n.wswo             <- n* 0.25
n.wsmo             <- n* 0.25 
n.mswo             <- n* 0.25 

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Formation model 
f.form             <- ~edges + concurrent +  nodemix("behavior", levels2=c(2,3,4,6,7,8,9))

#Target stats
targets            <- c( edges,            #total edges
                       (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0)      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships

#Now make the formation model which is conditional on the dissolution model 

fit2               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit2)
```

### FIT 2:  All groups equal size

Simulate the model and test output (code hidden- same as above)

```{r simulate2, echo=FALSE }
#dx.static     <- netdx(fit1, nsims = 1000, dynamic=FALSE)
#dx.static


#Simulate our model given the formation and dissolution we've established. 
dx_sim2             <- netdx(fit2, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior"))

#show what happened as a table
dx_sim2$stats.table.formation
plot(dx_sim2)
plot(dx_sim2, type  = "duration")
plot(dx_sim2, stats = c("concurrent"))
plot(dx_sim2, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim2$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim2$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim2$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout2         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(0.7,0.7,0.7)))

```

## Test 3: 4 groups, equal size, adding node factor

  We were close to our goal before, but not we can add nodefactor to specify that we want the mean degree among MSM to be different- in this case we want the overall mean degree to be 70%, but we want the mean degree of MSM to be 66%

```{r create_network3 , warning=FALSE , message=FALSE}


#Create populations for each size of our groups
n.msmo             <- n* 0.25
n.wswo             <- n* 0.25
n.wsmo             <- n* 0.25
n.mswo             <- n* 0.25

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Formation model 
f.form             <- ~edges + concurrent +  nodemix("behavior", levels2=c(2,3,4,6,7,8,9)) + 
                                             nodefactor("behavior", level=4)

#Target stats
targets            <- c( edges,            #total edges
                       (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,     #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                         n.msmo*0.66)      #mean degree of MSM should be 66% 

#Now make the formation model which is conditional on the dissolution model 

fit3               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit3)

```

### FIT 3:  Adding node factor

Simulate the model and test output (code hidden, same as above)

```{r simulate3, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim3             <- netdx(fit3, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior"))

#show what happened as a table
dx_sim3$stats.table.formation
plot(dx_sim3)
plot(dx_sim3, type  = "duration")
plot(dx_sim3, stats = c("concurrent"))
plot(dx_sim3, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim3$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim3$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim3$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout3         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(0.7,0.7,0.66)))

```


## Test 4: 4 groups, unequal size

  Now set MSM and WSW each to 10% of population size and those seeking opposite-sex partners to 80%. All using the same mean degree. 

```{r create_network4 , warning=FALSE , message=FALSE}


#Create populations for each size of our groups
n.msmo             <- n* 0.1
n.wswo             <- n* 0.1
n.wsmo             <- n* 0.4 
n.mswo             <- n* 0.4 

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Formation model 
f.form             <- ~edges + concurrent +  nodemix("behavior", levels2=c(2,3,4,6,7,8,9))

#Target stats
targets            <- c( edges,            #total edges
                       (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0)      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships

#Now make the formation model which is conditional on the dissolution model 

fit4               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit4)

```

### Fit 4: Unequal Size

```{r simulate4, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim4             <- netdx(fit4, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior"))

#show what happened as a table
dx_sim4$stats.table.formation
plot(dx_sim4)
plot(dx_sim4, type  = "duration")
plot(dx_sim4, stats = c("concurrent"))
plot(dx_sim4, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim4$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim4$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim4$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout4         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(NA,NA,NA)))

```


## Test 5: 4 groups, unequal size, adding nodefactor

  Set MSM and WSW each to 10% of population size and those seeking opposite-sex partners to 80%. Specify mean degree of 66% for MSM


```{r create_network5 , warning=FALSE , message=FALSE}

#Create populations for each size of our groups
n.msmo             <- n* 0.1
n.wswo             <- n* 0.1
n.wsmo             <- n* 0.4
n.mswo             <- n* 0.4 

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Formation model 
f.form             <- ~edges + concurrent +  nodemix("behavior", levels2=c(2,3,4,6,7,8,9))+ 
                                             nodefactor("behavior", level=4)

#Target stats
targets            <- c( edges,            #total edges
                       (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                          n.msmo*0.66)
#Now make the formation model which is conditional on the dissolution model 

fit5               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit5)

```


### Fit 5: Unequal Size + nodefactor

```{r simulate5, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim5             <- netdx(fit5, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior"))

#show what happened as a table
dx_sim5$stats.table.formation
plot(dx_sim5)
plot(dx_sim5, type  = "duration")
plot(dx_sim5, stats = c("concurrent"))
plot(dx_sim5, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim5$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim5$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim5$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout5         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(NA,0.7,0.66)))
```

## Test 6: 4 groups, unequal size, adding nodefactor, removing concurrency

  Set MSM and WSW each to 10% of population size and those seeking opposite-sex partners to 80%. 
  Specify mean degree of 66% for MSM. 
  Remove restrictions on the number of concurrent partners. 

```{r create_network6, warning=FALSE , message=FALSE}

# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Dissolution model 
#coef.diss          <- dissolution_coefs( dissolution = (~offset(edges)), 
#                                           duration  = c(30.0)) 

#Formation model 
f.form             <- ~edges + #concurrent +
                      nodemix("behavior", levels2=c(2,3,4,6,7,8,9))+ 
                      nodefactor("behavior", level=4)

#Target stats
targets            <- c( edges,            #total edges
                      # (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                          n.msmo*0.66)
#Now make the formation model which is conditional on the dissolution model 

fit6               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit6)

```


### Fit 6: Unequal Size w/o concurrency 
```{r simulate6, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim6             <- netdx(fit6, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior"))

#show what happened as a table
dx_sim6$stats.table.formation
plot(dx_sim6)
plot(dx_sim6, type  = "duration")
plot(dx_sim6, stats = c("concurrent"))
plot(dx_sim6, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim6$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim6$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim6$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout6         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(NA,0.7,0.66)))


#concurrency 
   round((dx_sim6$stats.table.formation$`Sim Mean`[2]/n),3)
```

## Test 7: 4 groups, unequal size, adding nodefactor, removing concurrency, adding WSW nodefactor

  Set MSM and WSW each to 10% of population size and those seeking opposite-sex partners to 80%. Specify mean degree of 66% for MSM. 
  Remove restrictions on the number of concurrent partners. 

```{r create_network7, warning=FALSE , message=FALSE}

#Formation model 
f.form             <- ~edges + #concurrent #+
                      nodemix("behavior", levels2=c(2,3,4,6,7,8,9))+ 
                      nodefactor("behavior", level=c(1,4))

#Target stats
targets            <- c( edges,            #total edges
                      # (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                          n.wswo*0.70,
                          n.msmo*0.66)
#Now make the formation model which is conditional on the dissolution model 

fit7               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit7)

```


### Fit 7: Unequal Size w/o concurrency + WSW

  Also report the percent concurrent nodes (vs. expected 5%)
  
```{r simulate7, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim7             <- netdx(fit7, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior", levels=c(-2)))

#show what happened as a table
dx_sim7$stats.table.formation
plot(dx_sim7)
plot(dx_sim7, type  = "duration")
plot(dx_sim7, stats = c("concurrent"))
plot(dx_sim7, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim7$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim7$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim7$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout7         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(0.70,0.7,0.66)))

#concurrency 
   round((dx_sim7$stats.table.formation$`Sim Mean`[2]/n),3)
   
```


## Test 8: 4 groups, unequal size, adding nodefactor, high concurrency, adding WSW nodefactor

  Set MSM and WSW each to 10% of population size and those seeking opposite-sex partners to 80%. 
  Specify mean degree of 66% for MSM and 70% for WSW. 
  Increase to 10% of the population having concurrent partnerships 

```{r create_network8 , warning=FALSE , message=FALSE}

concurrency        <- .08

#Formation model 
f.form             <- ~edges + concurrent +
                      nodemix("behavior", levels2=c(2,3,4,6,7,8,9))+ 
                      nodefactor("behavior", level=c(1,4))

#Target stats
targets            <- c( edges,            #total edges
                       (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                          n.wswo*0.70,
                          n.msmo*0.66)
#Now make the formation model which is conditional on the dissolution model 

fit8               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                             coef.diss    = coef.diss) 

summary(fit8)

```


### Fit 8: Unequal Size w/ high concurrency + WSW

  
```{r simulate8, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim8             <- netdx(fit8, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior", levels=c(-2)))

#show what happened as a table
dx_sim8$stats.table.formation
plot(dx_sim8)
plot(dx_sim8, type  = "duration")
plot(dx_sim8, stats = c("concurrent"))
plot(dx_sim8, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim8$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim8$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim8$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout8         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(0.70,0.7,0.66)))

#concurrency 
   round((dx_sim7$stats.table.formation$`Sim Mean`[2]/n),3)
   
```


## Test 9: Really small MSM pop (actual size)
  5% MSM + nodefactor + 8% concurrency


```{r create_network9 , warning=FALSE , message=FALSE}

set.seed(041788)
#Create populations for each size of our groups
n.msmo             <- n* 0.05
n.wswo             <- n* 0.05
n.wsmo             <- n* 0.45
n.mswo             <- n* 0.45 

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Formation model 
f.form             <- ~edges + #concurrent + 
                       nodemix("behavior", levels2=c(2,3,4,6,7,8,9))+ 
                       nodefactor("behavior", level=4)

#Target stats
targets            <- c( edges,            #total edges
                       #(n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                          n.msmo*0.66)
#Now make the formation model which is conditional on the dissolution model 

fit9               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox     = FALSE,
                          #set.control.ergm = control.ergm(MCMC.interval= 10000), 
                             coef.diss    = coef.diss)

summary(fit9)
```


### Fit 9: Small pop
  5% MSM + nodefactor + 8% concurrency

```{r simulate9, echo=FALSE }
set.seed(041788)

#Simulate our model given the formation and dissolution we've established. 
dx_sim9             <- netdx(fit9, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE,  
                           # set.control.ergm = control.simulate.ergm(MCMC.interval= 10000), 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior", levels=c(-2)))

#show what happened as a table
dx_sim9$stats.table.formation
plot(dx_sim9)
plot(dx_sim9, type  = "duration")
plot(dx_sim9, stats = c("concurrent"))
plot(dx_sim9, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim9$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim9$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim9$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout9         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(NA,0.7,0.66)))

#concurrency 
   round((dx_sim9$stats.table.formation$`Sim Mean`[2]/n),3)
   
   beep(2)
```


## Test 10:  Small MSM pop (actual size)
  5% MSM + nodefactor 


```{r create_network9 , warning=FALSE , message=FALSE}

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.wswo) , rep("MM", n.msmo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Formation model 
f.form             <- ~edges + #concurrent + 
                       nodemix("behavior", levels2=c(2,3,4,6,7,8,9))+ 
                       nodefactor("behavior", level=4)

#Dissolution model 
coef.diss          <- dissolution_coefs( dissolution = (~offset(edges)), 
                                           duration  = c(60.0)) 
#Target stats
targets            <- c( edges,            #total edges
                       #(n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,      #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                          n.msmo*0.66)

#Now make the formation model which is conditional on the dissolution model 

fit10               <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                             #edapprox    = FALSE,
                             coef.diss    = coef.diss, 
                         set.control.ergm = control.ergm(MCMC.interval= 2000))


summary(fit10)
```


### Fit 10: long duration- no restraint on concurrency 
  5% MSM + nodefactor + 8% concurrency

```{r simulate9, echo=FALSE }

#Simulate our model given the formation and dissolution we've established. 
dx_sim10             <- netdx(fit10, nsteps = (n.steps), nsims = n.sim, keep.tnetwork = FALSE, ncores = 8, keep.tedgelist = TRUE, 
                             nwstats.formula= ~edges +concurrent + nodemix("behavior") + nodefactor("behavior", levels=c(-2)))

#show what happened as a table
dx_sim10$stats.table.formation
plot(dx_sim10)
plot(dx_sim10, type  = "duration")
plot(dx_sim10, stats = c("concurrent"))
plot(dx_sim10, stats = c("nodefactor.behavior.MM"))

density_FF        <- (dx_sim10$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim10$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim10$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout10         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(NA,0.7,0.66)))

#concurrency 
   round((dx_sim10$stats.table.formation$`Sim Mean`[2]/n),3)
   
```
