---
title: "test_MCMC"
author: "Jenny Spencer"
date: "1/29/2020"
output: html_document
---

```{r setup}
#Just MSM
rm(list=ls())

library(EpiModel)   #the primary package we will be using to make our models 
library(beepr)
set.seed(041788)


#controls
n.sim      <- 3
n.steps    <- 500
```


## Test 1: MSM and WSW only 

We start with same-sex only (WSW and MSM) partnerships. We make each of these groups 50% of the total population. We assume a mean density of 70% and a concurrency rate of 5%. Mean relationship duration is 60 months. 

We set a limitation that WSW and MSM individuals cannot partner with each other- only within group partnerships are allowed. 


We start with same-sex only (WSW and MSM) and opposite-sex only (WSM and MSW) partnerships. To start we make each of these grousp 25% of the total population. We assume a mean density of 80% and a concurrency rate of 5%. Mean duration is 60 months. 

We define impossible combinations of sexual partnerships using nodemix on sexual behavior categories so that MSM can only partner with each other, WSW can only partner with each other and MSW/WSM can only partner across groups. 


```{r create_network1, warning=FALSE, message=FALSE}
   set.seed(04171988)

# # # # # # # # # # # #  Create Network  # # # # # # # # # # # # # # # # 

#Create a nework of 50/50 men and women 
n                  <- 20000

#Create populations for each size of our groups
n.msmo             <- n* 0.05 
n.wswo             <- n* 0.05
n.wsmo             <- n* 0.45 
n.mswo             <- n* 0.45 

#Network with n people, partnerships are not directed 
net1               <- network.initialize(n, directed=FALSE)

# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex", c(rep("F", n.wswo) , rep("M", n.msmo), rep("F", n.wsmo), rep("M", n.mswo) ))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#and behavior category
set.vertex.attribute(net1, "behavior", c(rep("FF", n.msmo) , rep("MM", n.wswo), rep("FM", n.wsmo), rep("MF", n.mswo) ))  


# # # # # # # # # # # #  Model Fit  # # # # # # # # # # # # # # # # 

#Define number of expected edges (density=0.7)
edges              <- (n *.7 * 0.5)   

#Overall concurrency is 5% 
concurrency        <- .05



#Formation model 
f.form             <- ~edges +
                 concurrent +  
                 nodemix("behavior", levels2=c(2,3,4,6,7,8,9)) + 
                 nodefactor("behavior", level=4)

#Target stats
targets            <- c( edges,            #total edges
                       (n*concurrency),    #concurrent
                        0,0,0,0,0,0,0,     #no FFxFM, FMxFM, FFxMF, MFxMF, FFxMM, FMxMM, MFxMM relationships
                         n.msmo*0.66)      #mean degree of MSM should be 66% 


#Dissolution model 
coef.diss          <- dissolution_coefs( dissolution = (~offset(edges)), 
                                           duration  = c(60.0)) 

#Now make the formation model which is conditional on the dissolution model 

fit1              <- netest(net1, 
                             formation    = f.form, 
                             target.stats = targets, 
                            #edapprox     = FALSE,
                         set.control.ergm = control.ergm(MCMC.interval= 10000), 
                             coef.diss    = coef.diss) 

summary(fit1)

```

### FIT 1:  MSM and WSW only 

Now we run a test of this model to see how we fit. 

```{r simulate1}
set.seed(04171988)

#Simulate our model given the formation and dissolution we've established. 
dx_sim1             <- netdx(fit1, nsteps = (n.steps), 
                                    nsims = n.sim, 
                            keep.tnetwork = FALSE, 
                                   ncores = 8, 
                         set.control.ergm = control.simulate.ergm(MCMC.interval= 10000), 
                           keep.tedgelist = TRUE, 
                          nwstats.formula = ~edges +concurrent + nodemix("behavior") + nodefactor("behavior") ) #+ degree(0:3))

#show what happened as a table
dx_sim1$stats.table.formation
plot(dx_sim1)
plot(dx_sim1, type  = "duration")

density_FF        <- (dx_sim1$stats.table.formation$`Sim Mean`[3]/n.wswo)*2
density_MF        <- (dx_sim1$stats.table.formation$`Sim Mean`[7]/n.wsmo)
density_MM        <- (dx_sim1$stats.table.formation$`Sim Mean`[12]/n.msmo)*2

(statsout1         <- data.frame("behavior"=c("FF", "MF", "MM"), 
                                "density observed"= round(c(density_FF, density_MF, density_MM),3),
                                "density target"=c(0.7,0.7,0.66)))

```

```{r concurrency_by}

#Check it out
tel_inf               <- data.frame(behav= get.vertex.attribute(net1, "behavior"),ID= (get.vertex.attribute(net1, "vertex.names")))
tel_dx                <- as.data.frame(dx_sim1, sim = 1) 
tel_dx$ID             <- tel_dx$tail
together1             <- merge(tel_inf, tel_dx, by.y="ID")
  
tel_dx$ID             <- tel_dx$head
together2             <- merge(tel_inf, tel_dx, by.y="ID")

together              <-rbind(together1,together2)
together$count        <- 1
together              <- together[which(together$terminus.censored==TRUE),]   

count_by_ID           <-aggregate(together[11], list(together$ID, together$behav), sum)


FF_conc               <- length(count_by_ID$count[which(count_by_ID$count>=2 & count_by_ID$Group.2=="FF")])/n.wswo
MF_conc               <- length(count_by_ID$count[which(count_by_ID$count>=2 & count_by_ID$Group.2=="MF")])/n.mswo
FM_conc               <- length(count_by_ID$count[which(count_by_ID$count>=2 & count_by_ID$Group.2=="FM")])/n.wsmo
MM_conc               <- length(count_by_ID$count[which(count_by_ID$count>=2 & count_by_ID$Group.2=="MM")])/n.msmo

count_by_behav        <-aggregate(count_by_ID[,3], list(count_by_ID$Group.2), mean)

```
