---
title: "Model_Creation_MSW"
author: "Jenny Spencer"
date: "9/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sessionInfo()

rm(list=ls())

library(EpiModel)    #the primary package we will be using to make our models 
library(ndtv)        #for the fancy videos
library(readxl)      #read in excel files 
library(tidyverse)   #Includes a number of shortcuts for data manipulation
library(beepr)       #makes the code beep when you get to it. Beep. 
library(kableExtra)  #for making tables look nice
library(mc2d)        #for using pert distribution

```

## Pull in Data for Sexual Behavior
Data for MSM comes largely from the National Survey of Family Growth (2011-2017). These data are cleaned & saved in the file *03.NSFG_cleaning_M.Rmd*. The final model inputs are saved in a list. 

```{r inputs_sex_behavior}

 load("./_2a_Inputs/msm_model_inputs.RData")

#Mean relationship duration
 msw_duration           <- msm_model_inputs$msw_duration$duration_1c
 df.t.byage_median      <- msm_model_inputs$byage_iqr
 df.t.byage_mean        <- msm_model_inputs$byage_mean
 v.t.agefirst_msw       <- msm_model_inputs$t.msw_agefirst
 df.mean_deg_msw        <- msm_model_inputs$msw_mean_deg
 abs_diff_msw           <- msm_model_inputs$abs_diff_behav[2,2]
 freq_msw               <- msm_model_inputs$behav_freq[2,2]
 
#Also establish network size - any other model-wide variables 
 n                       <- 1000
```


## Creating a Network

This is for testing the mechanics around network creation with my bisexual model 

First I want to create a network of `n` people. Then I create attributed assigned to those in the network. So far my attributes are: 

**sex**        Everyone is male in this model

**active2**    This indicates whether the individual is still active (alive) in the model. Starts as 1 for everyone. 

**position**   Men can have one of three positional preferences for sex "Exclusively Receptive", "Exclusively Insertive", or "Versatile" 

**age**        Uses age distribution of the US

**sex_active**  This is an indicator of whether an individual is sexually active (this keeps 4 YOs from having sex for example)

**age_active**  This is the age at which sex_active should switch from 0 to 1. 

I also create two variables that will store output from the model

**p_total** Number of sex partners - this starts as 0 and the model counts up for every new partner

**agefirst** The age at which an individual had their first sexual partner

      
```{r network_initiatlize}

# # # # Network Size and initialization # # # # # 

#Create populations for each size of our groups- for now everyone is MSM
n.mswo                  <- n*0.5
n.wsmo                  <- n*0.5


#Network with n people, partnerships are not directed 
net1                    <- network.initialize(n, directed=FALSE)


# # # # # # SEX # # # # 
#Add sex
set.vertex.attribute(net1, "sex",   c(sample(c("F", "M"), n, 
                                        replace= TRUE, 
                                        prob=c(0.5, 0.5))))

# # # # # # SEXUAL BEHAVIOR  # # # # 

#Add additional active counter
set.vertex.attribute(net1, "active2",   c(rep(1, n)))

# # # # # #  AGE   # # # # 

#calc age dist 
l.age                   <- c( "<1", "1-4", "5-9", "10-14", "15-20", "20-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59",   
                         "60-64", "65-69", "70-74", "75-79",  "80-85", "85+")

#make upper and lower limit variables- the actual age will be draw from a distribution within these so these will line up exactly. 
ll.age                  <- c( 0,   1,   5,   10,  15,  20,  25,  30,  35,  40,  45 , 50,   55,   60,   65,   70,   75,  80,  85)
ul.age                  <- c( 1,   5,   10,  15,  20,  25,  30,  35,  40,  45,  50,  55,   60,   65,   70,   75,   79,  85,  90)
    
i.age_dist              <-c(.04, .05, .05, .06, .06, .06, .06, .07, .07, .07, .06, .06, .06, .06, .06, .04, .04, .02 ,.01) 

#Three step process to add ages by year- 
    #First define upper and lower bounds
   age_ll               <-  c( rep(ll.age, (n*i.age_dist)))
   age_ul               <-  c(rep(ul.age, (n*i.age_dist)))
     
#Then draw n uniform distributions                                     
age_yrs                 <- runif(n, min=age_ll, max=age_ul)

#Finally, add specific age (years) to attribute
set.vertex.attribute(net1, "age", round(age_yrs, 1)) 

#Look at our age distribution to check that it looks right
#hist(get.vertex.attribute(net1, "age"))

#Randomly assign everyone an age for onset of sexual behavior- this is the age when they can start finding partners so it will be slightly younger than the age at which they are first partnered

age_active              <- c(rep(9, n)) #rpert(n.msmo, min=8, mode=15, max=25, shape=10))

set.vertex.attribute(net1, "age.actv", age_active)

#And a variable to indicate if the individual is sexually active 
check.sex.active        <- ifelse(age_yrs>=age_active, 1, 0)
set.vertex.attribute(net1, "sex.actv", check.sex.active)


#Storage variables 
set.vertex.attribute(net1, "p_total",   c(rep(0, n)))

set.vertex.attribute(net1, "agefirst", NA) 

```


###Deaths and Natural History Variables 

Here we pull in a lifetable to use as mortality estimates 

```{r inputs_deaths_nh}


df.lifetable            <- data.frame(read_excel("./_2A_Inputs/mortality.xlsx", sheet="Sheet1")) 


v.mortality_rate_m      <- df.lifetable$Male
v.mortality_rate_f      <- df.lifetable$Female

# rate per person, per week
v.mrm_pp_pw             <- v.mortality_rate_m / 1e5 / 12
v.mrf_pp_pw             <- v.mortality_rate_f / 1e5 / 12

# Build out a mortality rate vector
     
v.age_spans             <-c(1,4,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5)
     
v.mort                  <- rep(v.mrm_pp_pw, times = v.age_spans)
v.mort_f                <- rep(v.mrf_pp_pw, times = v.age_spans)
     
df.mort_all             <- (data.frame(c(0:89), v.mort, v.mort_f))
colnames(df.mort_all)   <-  c("Age", "Male", "Female")
                           
   
## Need data on regression----
                     
```


Then we create our target stats. We will define the total number of *edges* (partnerships) at any given point, as well as the number of nodes we expect to be in multiple partnerships concurrently. We will also set restrictions by position- for example, two exclusively receptive men should never form a partnership. Finally, if we don't set expectations by position we end up with a lot more versatile nodes in relationships- so I set an expectation for this value. 

```{r target_stats}
#This is all stats for men- also have 
mean_degree             <- as.vector((df.mean_deg_msw[2,1] + (2*df.mean_deg_msw[3,1]))/100)*(mean(check.sex.active))
n.concurrent            <- as.vector(df.mean_deg_msw[3,1]/100)


#Total number of men x mean degree x 0.5 (1 edge per 2 people)
edges                   <- (n*mean_degree*0.5)

#Then stats based on this- first edges total, the concurrent, then all possible combinations that should be impossible 
#(ie, two men who only have sex with women can never have a partnership)
# Impossible combinations: FB.FM, FF.FM, FM.FM, FF.MB, FF.MF, MB.MF, MF.MF, FB.MM, FF.MM, FM.MM, MF.MM

targets                 <- c( edges ,            #total edges
                           (n*n.concurrent),     #concurrent nodes  
                            edges*abs_diff_msw,  #age assortiveness
                              0,                 #No FxF partnerships
                              0,                 #No MxM partnerships
                              0)                 #Those who aren't sexually active can't have sex
```

###Model Fit

Now we use the ERGM componants to fit a model. We need the dissolution model (chance that a relationship ends) and the formation model (change that two nodes form a new relationship). Our formation model will match the target stats described above. Our dissolution model will consider only relationship duration and adjust this by the death rate. 

```{r model_fit}

# set.seed(041789)

#Dissolution Model
f.coef.diss             <- dissolution_coefs( dissolution = (~offset(edges)),
                                               duration   = c(msw_duration),
                                                d.rate    = mean(df.mort_all$Male))

#Formation model
 f.form                 <- ~edges  +  
                           concurrent  +
                           absdiff("age") + 
                          nodemix("sex", levels2=c(1,3))  + 
                          nodefactor("sex.actv", levels=c(1))  
                         # #degree(4)
	
	
#Now make the formation model which is conditional on the dissolution model 
fit1                    <- netest(net1,  
                                 formation    = f.form, 
                                 target.stats = targets, 
                                 #edapprox     = FALSE,
                                 coef.diss    = f.coef.diss) 

summary(fit1)

#to test
  #dx.static     <- netdx(fit1, nsims = 1000, dynamic=FALSE)
  #dx.static
  
  
```
Simulate our model over 1000 time steps to see if it matches our expectation.
```{r simulate, echo=FALSE}
set.seed(041788)

#Simulate our model given the formation and dissolution we've established. Run for 1000 steps but just 1 simulation of it
dx_sim                  <- netdx(fit1, nsteps = (1000), 
                                 nsims = 3, 
                                 keep.tnetwork = FALSE, 
                                 ncores = 3, 
                                 keep.tedgelist = TRUE, 
                                 nwstats.formula= ~edges + 
                                                  concurrent + 
                                                  absdiff("age") + 
                                                  degree(c(0,1,2,3)))

#show what happened as a table
dx_sim$stats.table.formation

nwstats1            <- get_nwstats(dx_sim, sim=1)

#mcmc.diagnostics(fit1$fit) 
```

###Model Diagnostics 

Check to make sure our model matches up with all the things we think it should

```{r model_diagnostics}
#we can also make fit graphs 
plot(dx_sim, type  = "formation" )
plot(dx_sim, type  = "duration")
plot(dx_sim, stats = c("edges", "concurrent"))

#Check concurrency by group 
tel_inf                 <- data.frame(behav= get.vertex.attribute(net1, "behavior"),ID= (get.vertex.attribute(net1, "vertex.names")))
tel_dx                  <- as.data.frame(dx_sim, sim = 1) 
tel_dx$ID               <- tel_dx$tail
together1               <- merge(tel_inf, tel_dx, by.y="ID")
    
tel_dx$ID               <- tel_dx$head
together2               <- merge(tel_inf, tel_dx, by.y="ID")
  
together                <-rbind(together1,together2)
together$count          <- 1
together                <- together[which(together$terminus.censored==TRUE),]   
  
count_by_ID             <-aggregate(together[11], list(together$ID, together$behav), sum)
  

```


##Running an Infection Model

Now that we have a basic partnership model, we can run an infection over it. 

Using the basic epimodel infection for now- need to add in more complex infection dynamics 

```{r infection_model}

#source("./05_Model_Functions.R")

  simtime               <- 1500
  n.sims                <- 1

 # Parameterizing an SIS epidemic
 param                  <- param.net( inf.prob = 0.05,
                                 # mortality.rates = (df.mort_all),
                                #    birth.rate = (mean(df.mort_all$Male)), 
                                #    rec.rate.a = v.rec.month.A, 
                                #    rec.rate.g = v.rec.month.G, 
                                    rec.rate   = 0.01,
                                    act.rate   = freq_msw) #,
                                #    inf.prob.r = 0.33, 
                                #    inf.prob.i = 0.05)
 order_list             <- c("infection.FUN", "aging.FUN", "departures.FUN", "recovery.FUN", "arrivals.FUN", "epi.FUN")
 
 # Initial conditions
 init                   <- init.net(i.num = n*0.1)
 
 start.time             <- Sys.time()
 # Control setting      
 control                <- control.net(type = "SIS", 
                                      nsims = n.sims, 
                                     ncores = 8,
                                     nsteps = simtime, 
                        #       infection.FUN = f.inf_msm,
                        #           aging.FUN = age.func,
                        #        recovery.FUN = f.recovery,
                        #      departures.FUN = d.func,
                        #        arrivals.FUN = b.func,
                        #             epi.FUN = epi.func, 
                              keep.tedgelist = TRUE,
                               keep.tnetwork = TRUE,  
                                delete.nodes = FALSE, 
                                      depend = TRUE,
                           #    module.order = order_list,
                                     verbose = FALSE)

 
# Run the network model simulation with netsim
sim_short               <- netsim(fit1, param, init, control)
      
 stop.time              <- Sys.time()
(total.time             <- stop.time - start.time)

#plot(sim_short)

 #put the data from this simulation
out_sim                 <- as.data.frame(sim_short)
tel_sim                 <- as.data.frame(sim_short$network$sim1) 

 #Graph of age at sexual behavior onset
 #ggplot()+ geom_point(aes(x=sex_age, y=age_out, col=sex_out))

#Age distribution of final network
 hist(get.vertex.attribute(sim_short$network$sim1, "age"))

     n2                 <- network.size(sim_short$network$sim1)
     
     plot(sim_short)

```
